Recursive algorithms, branching coefficients and applications

### 2010-07-09 AffineLieAlgebras/InformalNotes/article.tex
IOP work

\documentclass[12pt]{iopart}
\usepackage{ucs}
%\usepackage{amsmath,amssymb,amsthm}
\usepackage{iopams,amssymb,amsthm}
%\usepackage{pb-diagram}
\usepackage{multicol}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
%\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
%\pagestyle{plain}
%\usepackage[unicode,verbose,plainpages=false]{hyperref}
\usepackage{hyperref}

@@

\begin{document}
% \pagenumbering{alph}
% \thispagestyle{empty}
% 
% \begin{center}
% {\Large \bf SAINT-PETERSBURG STATE\\[0.5cm] UNIVERSITY}
% \end{center}
% \vskip 1 cm
% \begin{flushright}
% {\large \bf SPbU-IP-10-03}
% \end{flushright}
% \hfill {}
% \vskip 1 cm
% \begin{center}
% {\Huge \bf Recursive algorithms, branching coefficients \\ and applications\\[0.5cm]
% }
% \end{center}
% \vskip 1.0 cm
% \begin{center}
% {\Large \bf
% Vladimir Lyakhovsky\\[2mm]
% Anton Nazarov}
% \end{center}
% \vfill
% \begin{center}
% {\large Department of Theoretical Physics\\
% }
% \end{center}
% \vfill
% \begin{center}
% SAINT-PETERSBURG \\
% 2010
% \end{center}
% 
% \newpage
% 
% \pagenumbering{arabic}
\title{Recursive algorithms, branching coefficients and applications}
\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$} 
\address{$^{1,2}$ Theoretical Department, SPb State University,
198904, Sankt-Petersburg, Russia }
\eads{$^1$ \mailto{lyakh1507@nm.ru}, $^2$ \mailto{antonnaz@gmail.com}}
% \thanks{ Supported by
%  RFFI grant N 09-01-00504 and the National Project RNP.2.1.1./1575 }\\
% 
% \thanks{ Supported by
% the National Project RNP.2.1.1./1575 }

@@

The branching problem for affine Lie algebras emerges in conformal field theory, for example, in the construction of modular-invariant partition functions \cite{difrancesco1997cft}. Recently the problem of the conformal embeddings was considered in the paper \cite{coquereaux2008conformal}.

@@

Usually only the maximal reductive subalgebras are considered since the case of non-maximal subalgebra
can be obtained using the chain of maximal injections. In this paper we find the recurrent properties
for branching coefficients that generalise the relations obtained earlier (see the paper \cite{ilyin812pbc}
and the references therein) to the case of non-maximal reductive subalgebra. The result is formulated in
terms of the new injection fan called "the subtracted fan". Using this new tools we formulate a simple and
explicit algorithm for computations of branching coefficients which is applicable to the non-maximal
subalgebras of finite-dimensional and affine Lie algebras.

@@

$\lambda =\left( \co{\lambda };k;n\right) $ --- the
decomposition of an affine weight indicating the finite part $\co{\lambda }$, level $k$ and grade $n$\ .

@@

$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
\xi \in P$ $\left( \mbox{resp. }\in P_{\frak{a}}\right) $ for the module $%
L^{\mu }$ $\left( \mbox{resp. }L_{\frak{a}}^{\nu }\right) $ with the
coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
\circ (\nu +\rho _{a})-\rho _{a}}$ ),

@@

$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
\mathrm{{mult}\left( \alpha \right) }}}=\frac{\Psi ^{\left( \mu \right) }}{%
\Psi ^{\left( 0\right) }}$ --- the Weyl-Kac formula.

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
mult}\left( \alpha \right) }}=\Psi ^{\left( 0\right) }\quad $

\noindent $\left( \mbox{resp. }R_{\frak{a}}:=\prod_{\alpha \in \Delta _{%
\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}\mathrm{%
\left( \alpha \right) }}=\Psi _{\frak{a}}^{\left( 0\right) }\right) $--- the
denominator.

$  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$ --- the module decomposition with respect to $\frak{a}\longrightarrow \frak{g}$;

$b^{(\mu)}_{\nu}$ --- the branching coefficients;

\begin{equation}
  \label{eq:21}
  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda }
\end{equation}

 $k_{\lambda}$ --- the anomalous branching coefficients, notice that
\begin{equation*}
%  \label{eq:20}
  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}}
\end{equation*}

@@

Our aim is to demonstrate that despite the zeros arriving in the Weyl denominator $R$
(when it is projected to the $P_{\mathfrak{a}}$) the injection fan technique \cite{ilyin812pbc} can be properly modified.
The result is the generalized recurrent relation for anomalous branching
coefficients \ref{eq:21}:
\begin{equation}
  \label{eq:1}
  \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
\left.
+\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)
  \end{array}
   \end{equation}
Here $\mathfrak{a}_{\bot}$ is the subalgebra fixed by those roots of $\mathfrak{g}$ that are
orthogonal $P_{\mathfrak{a}}$, $W_{\bot}$ is the corresponding Weyl group,
$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion
of the product $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$
is the multiplicity of $e^{\gamma}$ in this expansion.
In the next subsection we study the situation in details and prove the relation \ref{eq:1}.

@@

Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
\begin{equation*}
%  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation*}
The Weyl-Kac character formula leads to
the relation
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
  {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
  e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
  {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{equation}

Consider the positive roots $\alpha\in \Delta$ orthogonal to $P_{\mathfrak{a}}$. Denote the subset of such roots by $\Delta^{+}_{\bot}
=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
Notice that if $\Delta^{+}_{\bot}\neq \emptyset$ the corresponding Weyl reflections
generate a subgroup $W_{\bot}$ of the group $W$. Consider the roots $\alpha,\;
\beta\in \Delta^{+}_{\bot}$ and the corresponding reflections
$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since the roots in $\Delta_{\mathfrak{a}}$
are invariant with respect to $\omega_{\alpha}, \; \omega_{\beta}$ they
are also invariant under the product $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$
and the subgroup $W_{\bot}$ preserves the roots in $\Delta_{\mathfrak{a}}$.
The system $\Delta_{\bot}$
can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.

Now we are to find out when the subset $\Delta^{+}_{\bot}$ is non-empty with the non-trivial subgroup $W_{\bot}$ and the subalgebra $\mathfrak{a}_{\bot}$.

If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then $r_{\mathfrak{a}}=r$ and
 $\Delta^{+}_{\bot}$ is empty.
On the other hand
non-maximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
through the chain of maximal embeddings
$\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
The maximal regular embeddings can be described by the elimination of one or two roots
from the extended Dynkin diagram of the algebra. When the process gives us
non-connected diagrams we immediately fix the roots orthogonal to $P_{\mathfrak{a}}$.  The complete classification of the regular subalgebras for affine Lie algebras can be found in the recent paper \cite{1751-8121-41-36-365204}.

For a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ when both $\mathfrak{a}$ and $\mathfrak{g}$ are simple the sufficient condition for $\Delta^{+}_{\bot}$ to be nontrivial can be formulated as follows:
if the Dynkin diagram of $\mathfrak{g}$ contains the disconnected
subdiagrams of $\mathfrak{a}$ and of some subalgebras $\{\mathfrak{\bar{a}}_j\}$
then the subset $\Delta_{\bot}$ is non-empty,
subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and
$\left\{\mathfrak{\bar{a}}_j\right\}$ are the subalgebras of $\mathfrak{a}_{\bot}$.

@@

Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$ must not form a direct sum in $\mathfrak{g}$.  
Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
 Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the remaining nodes of the diagram of $\mathfrak{g}$. The remaining diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ with $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether $\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\mathfrak{\bar{a}}$ but the linear combinations of them. The answer is positive  when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$. Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$. 
\begin{table}[ph]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{table1_1(l).eps} & \includegraphics{table1_1(r).eps} \\
  \hline                                                                     
  $B_n$ & \includegraphics{table1_2(l).eps} & \includegraphics{table1_2(r).eps} \\
  \hline                                                                     
  $C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps} \\
  \hline                                                                     
  $D_n$ & \includegraphics{table1_4(l).eps} & \includegraphics{table1_4(r).eps} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}
If $\mathfrak{a}=B_{r_{\mathfrak{a}}}$  we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$. This is the only case where the simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.

Using the existing classification of maximal special subalgebras in classical Lie algebras \cite{dynkin1952semisimple} we have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
\begin{equation*}
%  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}\\
  \end{array}
\end{equation*}
Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.

Now consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$ can be written as
\begin{equation*}
%  \label{eq:41}
  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
\end{equation*}
Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.

>>>>

\documentclass[12pt]{iopart}
%\usepackage{ucs}
%\usepackage{amsmath,amssymb,amsthm}
\usepackage{iopams,amssymb,amsthm}
%\usepackage{pb-diagram}
\usepackage{multicol}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
%\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
%\pagestyle{plain}
%\usepackage[unicode,verbose,plainpages=false]{hyperref}
\usepackage{hyperref}

@@

\begin{document}

\title{Recursive algorithms, branching coefficients and applications}
\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}
\address{$^{1,2}$ Theoretical Department, SPb State University,
198904, Sankt-Petersburg, Russia }
\eads{$^1$ \mailto{lyakh1507@nm.ru}, $^2$ \mailto{antonnaz@gmail.com}}

@@

The branching problem for affine Lie algebras emerges in conformal field theory, for example,
in the construction of modular-invariant partition functions \cite{difrancesco1997cft}.
Recently the problem of conformal embeddings was considered in the paper \cite{coquereaux2008conformal}.

@@

Usually only the maximal reductive subalgebras are considered since the case of non-maximal subalgebra
can be obtained using the chain of maximal injections. In this paper we find the recurrent properties
for branching coefficients that generalize the relations obtained earlier (see the paper \cite{ilyin812pbc}
and the references therein) to the case of non-maximal reductive subalgebra. The result is formulated in
terms of the new injection fan called "the subtracted fan". Using this new tools we formulate a simple and
explicit algorithm for computations of branching coefficients which is applicable to the non-maximal
subalgebras of finite-dimensional and affine Lie algebras.

@@

$\lambda =\left( \co{\lambda };k;n\right) $ --- the
decomposition of an affine weight indicating the finite part $\co{\lambda }$, level $k$ and grade $n$;

@@

$\widehat{\Psi ^{\left( \mu \right) }}$ $\left( \widehat{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}\right) $ --- the set of singular weights $%
\xi \in P$ $\left( \mbox{resp. }\in P_{\frak{a}}\right) $ for the module $%
L^{\mu }$ $\left( \mbox{resp. }L_{\frak{a}}^{\nu }\right) $ with the
coordinates $\left( \co{\xi },k,n,\epsilon \left( w\left( \xi
\right) \right) \right) \mid _{\xi =w\left( \xi \right) \circ (\mu +\rho
)-\rho },$ (resp. $\left( \co{\xi },k,n,\epsilon \left(
w_{a}\left( \xi \right) \right) \right) \mid _{\xi =w_{a}\left( \xi \right)
\circ (\nu +\rho _{a})-\rho _{a}}$ );

@@

$ch\left( L^{\mu }\right) =\frac{\sum_{w\in W}\epsilon (w)e^{w\circ (\mu
+\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{%
\mathrm{{mult}\left( \alpha \right) }}}=\frac{\Psi ^{\left( \mu \right) }}{%
\Psi ^{\left( 0\right) }}$ --- the Weyl-Kac formula;

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
mult}\left( \alpha \right) }}=\Psi ^{\left( 0\right) }\quad $;

\noindent $\left( \mbox{resp. }R_{\frak{a}}:=\prod_{\alpha \in \Delta _{%
\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}}\mathrm{%
\left( \alpha \right) }}=\Psi _{\frak{a}}^{\left( 0\right) }\right) $--- the
denominator;

$  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus
\limits_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }$
 --- the module decomposition with respect to $\frak{a}\longrightarrow \frak{g}$;

$b^{(\mu)}_{\nu}$ --- the branching coefficients,

\begin{equation}
  \label{eq:21}
  \sum_{\nu \in \bar{C_{\mathfrak{a}}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda };
\end{equation}

 $k_{\lambda}$ --- the anomalous branching coefficients, notice that
\begin{equation*}
%  \label{eq:20}
  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}};
\end{equation*}

@@

Our aim is to demonstrate that despite the zeros arriving in the Weyl denominator $R$
(when it is projected to $P_{\mathfrak{a}}$) the injection fan technique \cite{ilyin812pbc} can be properly modified.
The result is the generalized recurrent relation for anomalous branching
coefficients (\ref{eq:21}):
\begin{equation}
  \label{eq:1}
  \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
  {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
  \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
\left.
+\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right).
  \end{array}
   \end{equation}
Here $\mathfrak{a}_{\bot}$ is the subalgebra fixed by those roots of $\mathfrak{g}$ that are
orthogonal to $P_{\mathfrak{a}}$, $W_{\bot}$ is the corresponding Weyl group,
$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion
of the product $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$
is the multiplicity of $e^{\gamma}$ in this expansion.
In the next subsection we study the situation in details and prove the relation (\ref{eq:1}).

@@

Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
\begin{equation*}
%  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}.
\end{equation*}
The Weyl-Kac character formula leads to
the relation
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
  {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
  e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
  {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
\end{equation}

Consider the positive roots $\alpha\in \Delta$ orthogonal to $P_{\mathfrak{a}}$.
Denote the subset of such roots by $\Delta^{+}_{\bot}
=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
Notice that if $\Delta^{+}_{\bot}\neq \emptyset$ the corresponding Weyl reflections
generate a subgroup $W_{\bot}$ of the group $W$. Consider the roots $\alpha,\;
\beta\in \Delta^{+}_{\bot}$ and the corresponding reflections
$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since the roots in $\Delta_{\mathfrak{a}}$
are invariant with respect to $\omega_{\alpha}, \; \omega_{\beta}$
and $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$
the subgroup $W_{\bot}$ preserves the roots in $\Delta_{\mathfrak{a}}$.
The subsystem $\Delta_{\bot}$
can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.

Now we are to find out when the subset $\Delta^{+}_{\bot}$ is nonempty
with the nontrivial subgroup $W_{\bot}$ and the subalgebra $\mathfrak{a}_{\bot}$.

If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then $r_{\mathfrak{a}}=r$ and
 $\Delta^{+}_{\bot}$ is empty.
On the other hand
nonmaximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
through the chain of maximal embeddings
$\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
The maximal regular embeddings can be described by the elimination of one or two roots
from the extended Dynkin diagram of the algebra. When the process gives us
nonconnected diagrams we immediately fix the roots orthogonal to $P_{\mathfrak{a}}$.
The complete classification of the regular subalgebras for affine Lie algebras can be
found in the recent paper \cite{1751-8121-41-36-365204}.

For a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ when both $\mathfrak{a}$
and $\mathfrak{g}$ are simple the sufficient condition for $\Delta^{+}_{\bot}$ to be
nontrivial can be formulated as follows:
if the Dynkin diagram of $\mathfrak{g}$ contains the disconnected
subdiagrams of $\mathfrak{a}$ and of some subalgebras $\{\mathfrak{\bar{a}}_j\}$
then the subset $\Delta_{\bot}$ is not empty,
subalgebra $\mathfrak{a}_{\bot}$ is nontrivial and
$\left\{\mathfrak{\bar{a}}_j\right\}$ are the subalgebras of $\mathfrak{a}_{\bot}$.

@@

Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$
must not form a direct sum in $\mathfrak{g}$.
Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both
algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a
subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with
the remaining nodes of the diagram of $\mathfrak{g}$. The result is the diagram of
the algebra $\bar{\mathfrak{a}}$ with $\mathrm{rank}(\bar{\mathfrak{a}}) =
\mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that
$\bar{\mathfrak{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether
$\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\bar{\mathfrak{a}}$
but the linear combinations of them. The answer is positive  when the set of angles
between the roots of $\bar{\mathfrak{a}}$ does not contain all the angles between
the roots of $\mathfrak{a}$.
Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional
roots of $\mathfrak{a}_{\bot}$.
\begin{table}[ph]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ &
  Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{table1_1(l).eps} & \includegraphics{table1_1(r).eps} \\
  \hline
  $B_n$ & \includegraphics{table1_2(l).eps} & \includegraphics{table1_2(r).eps} \\
  \hline
  $C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps} \\
  \hline
  $D_n$ & \includegraphics{table1_4(l).eps} & \includegraphics{table1_4(r).eps} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}
If $\mathfrak{a}=B_{r_{\mathfrak{a}}}$  we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\;
1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
This is the only case where the simple roots of $\mathfrak{a}_{\bot}$ can not be
obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.

Using the existing classification of maximal special subalgebras in classical Lie algebras
\cite{dynkin1952semisimple} we have the following pairs of the orthogonal
subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
\begin{equation*}
%  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}.\\
  \end{array}
\end{equation*}

Now consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and
its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
can be written as
\begin{equation*}
%  \label{eq:41}
  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}=
  \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega)
  e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}
  {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
\end{equation*}
Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$
is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$
with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.
